Analysis

### 2024-03-21 production/prod_analysis-fix-t5.Rmd
change orden interactions and captions graphs

```{r}
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))
df_study1 <- df_study_long_t6_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, des_perc, merit_effort, merit_talent,
                                               educ, quintil1:sexo)
df_study1 <- df_study1[complete.cases(df_study1$segmento), ]

@@

```{r alluvial}
alluvial_justeduc <- ggplot(datos.justeduc, aes(x = ola, fill = just_educ, stratum = just_educ,
                             alluvium = idencuesta, y = porcentaje))+
    ggalluvial::geom_flow(alpha = .66) + 
    ggalluvial::geom_stratum(linetype = 0) +
    scale_y_continuous(labels = scales::percent) + 
    ylab(label = NULL) +
    xlab(label = NULL) + 
    theme(#legend.position = 'top',
          legend.title = element_blank(),
          plot.caption = element_text(hjust = 0)) +
    scale_fill_manual(values = colors) +
    geom_shadowtext(data = etiquetas.justeduc, 
              aes(label = ifelse(porcentaje > 0 , scales::percent(porcentaje, accuracy = .1),"")),
              position = position_stack(vjust = .5),
              show.legend = FALSE,
              size = 4,
              color = rep('white'),
              bg.colour='grey30')+
  scale_x_discrete(labels = c(2016, 2017, 2018, 2019, 2022))

@@

ggsave(alluvial_justeduc, file="output/graphs/alluvial_dep.png", height = 7, width = 8)
```

```{r bivariate-plots}
df_study1 <- df_study_long_t6_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, des_perc, merit_effort, merit_talent,
                                               educ, quintil1:sexo)
merit_plot <- df_study1 %>% 
  select(merit_effort, merit_talent, des_perc, just_educ) %>% 
  sjPlot::plot_stackfrq(weight.by = df_study1$ponderador_long_total,
                        expand.grid =TRUE,
                      geom.colors = "PuBu",
                      show.total = FALSE, 
                      vjust=rep(c("bottom", "top", "bottom", "top", "bottom"),4),
                      legend.labels = c("Strongly disagree", "Disagree", "Neither agree
nor disagree", "Agree", "Strongly agree"),
                      axis.labels = c("Merit effort", "Merit talent", "Inequality 
perception", "Justification of 
educational inequality")
                      ) +
  theme_light() +
  theme(legend.position="bottom", text = element_text(size = 14))
merit_plot

@@

## Crear el gráfico principal
years_plot <- ggplot(vars_years, aes(ola, value, color = variable, shape = variable)) +
  theme_bw(base_size = 14) +
  geom_point(size = 4) +
  geom_line(aes(group = variable)) +
  geom_errorbar(aes(ymin = value_low, ymax = value_upp), width = 0.2) +
  ylab("Mean") +
  xlab("Wave") +
  ylim(1, 5) +
  scale_x_discrete(labels = categorias_x) +
  scale_color_discrete(labels = categorias_z, name = "Variable") +
  scale_shape_manual(labels = categorias_z, name = "Variable", values = c("square", "circle", "triangle", "diamond")) +
  theme(legend.position = "none") +  # Desactivar la leyenda por ahora
  coord_cartesian(xlim = c(1, 6)) +  # Ampliar el eje x
  scale_x_discrete(labels = c(2016, 2017, 2018, 2019, 2022, ""))  # Personalizar etiquetas del eje x

@@

# Añadir etiquetas personalizadas
years_plot <- years_plot +
  geom_point(data = label_data, aes(label_x - 0.05, label_y, color = variable, shape = variable), size = 4) +  # Capa de puntos para los símbolos de forma
  geom_text(data = label_data, aes(label_x, label_y, label = variable), color = "black", hjust = 0, nudge_x = 0.05, nudge_y = 0, size = 4)  # Etiquetas

@@

ggsave("output/graphs/years_plot.png", plot = years_plot, height = 7, width = 7, dpi = 300)

@@

```{r cor-plot, fig.dim=c(10,6)}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               sjPlot,
               sjmisc,
               summarytools,
               lavaan
               )
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))

# Full sample_______________________________________________________________________
mat_full<- 
df_study_long_t6_comunas %>%
  # filter(ola==1) %>%
  select(just_educ, # distributive justice
         des_perc,
         merit_effort, merit_talent # meritocracy
         ) %>% 
  psych::mixedCor()

cor_full <- as.matrix(mat_full$rho)
diag(cor_full) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_full) <- c("A. Justification of educational inequality",
                        "B. Inequality perception",
                     "C. People are rewarded for their efforts",
                     "D. People are rewarded for their intelligence")
#set Column names of the matrix
colnames(cor_full) <-c("(A)", "(B)","(C)","(D)")
#Plot the matrix using corrplot
png("output/graphs/corr.png",width=600,height=300, pointsize = 10)
corrplot::corrplot(cor_full,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-")
dev.off()
# Wave 1_______________________________________________________________________
mat_1<- 
df_study1_long_comunas %>%
  filter(ola==1) %>%
  select(just_educ, # distributive justice
         merit_effort, merit_talent, # meritocracy
         ahead_family, ahead_ambition, ahead_educ, ahead_hardwork # go ahead
         ) %>% 
  psych::mixedCor()

@@

omit <- "(education)|(ess)"
texreg::htmlreg(list(educ0, educ1, educ2, educ3, educ4, educ5, educ6),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. Model 3 to 7 are controlled by educational level, and subjective social status with no significant effects.", 
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave 2017 <br> <i>(Ref. Wave 2016)</i>",
                                      "Wave 2018",
                                      "Wave 2019",
                                      "Wave 2022",
                                      "Wave",
                                      "Wave^2",
                                      "Quintile 2 <br> <i>(Ref. Quintile 1)</i>",
                                      "Quintile 3",
                                      "Quintile 4",
                                      "Quintile 5",
                                      "Quintile NA",
                                      "Age 30-49 <br> <i>(Ref. 18-29)</i>",
                                      "Age 50-64",
                                      "Age 65 o más",
                                      "Gender <br> <i>(Ref. Male)</i>",
                                      "Pol. pos: Center <br> <i>(Ref. Left)</i>",
                                      "Pol. pos: Right",
                                      "Pol. pos: Does not identify",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: effort" ),
                file = "output/tables/table1-individuales-pond-v2.html")
          #omit.coef = omit

@@

# Hipotesis
h1b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort"
h2b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+des_perc*ola_2"
h3b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*merit_talent"
h4b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+merit_effort*ola_2"
h5b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*pos_id"
h6b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*sexo"
h7b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*quintil1"
h8b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*edad"

# A. justification educational inequality
educ1 <- lmer(formula(paste0("just_educ~",h1b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ2 <- lmer(formula(paste0("just_educ~",h2b,"+(ola+ola_2+des_perc|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ3 <- lmer(formula(paste0("just_educ~",h3b,"+(ola+ola_2+merit_talent|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ4 <- lmer(formula(paste0("just_educ~",h4b,"+(ola+ola_2+merit_effort|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ5 <- lmer(formula(paste0("just_educ~",h5b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ6 <- lmer(formula(paste0("just_educ~",h6b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ7 <- lmer(formula(paste0("just_educ~",h7b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ8 <- lmer(formula(paste0("just_educ~",h8b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)

# table 3: interacciones
omit <- "(education)|(ess)"
texreg::htmlreg(list(educ1,educ2,educ3,educ4,educ5,educ6,educ7,educ8),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. All the models are controlled by educational level, subjective social status, political position, and income quintile",
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave",
                                      "Wave^2", 
                                      "Quintile 2 <br> <i>(Ref. Quintile 1)</i>",
                                      "Quintile 3",
                                      "Quintile 4",
                                      "Quintile 5",
                                      "Quintile NA",
                                      "Age 30-49 <br> <i>(Ref. 18-29)</i>",
                                      "Age 50-64",
                                      "Age 65 o más",
                                      "Gender <br> <i>(Ref. Male)</i>",
                                      "Pol. pos: Center <br> <i>(Ref. Left)</i>",
                                      "Pol. pos: Right",
                                      "Pol. pos: Does not identify",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: effort",
                                      "Wave^2 * Inequality perception",
                                      "Wave^2 * Merit: talent",
                                      "Wave^2 * Merit: effort",
                                      "Wave^2 * Center",
                                      "Wave^2 * Right",
                                      "Wave^2 * Does not identify",
                                      "Wave^2 * gender",
                                      "Wave^2 * Quintile 2",
                                      "Wave^2 * Quintile 3",
                                      "Wave^2 * Quintile 4",
                                      "Wave^2 * Quintile 5",
                                      "Wave^2 * Quintile NA",
                                      "Wave^2 * Age 30-49",
                                      "Wave^2 * Age 50-64",
                                      "Wave^2 * Age 65 or more"
                                      ),
                file = "output/tables/table3-interac_pond.html")
          #omit.coef = omit

>>>>

```{r}
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))
df_study1 <- df_study_long_t6_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, des_perc, merit_effort, merit_talent,
                                               educ, quintil1:sexo) %>% na.omit()
df_study1 <- df_study1[complete.cases(df_study1$segmento), ]

@@

```{r alluvial}
colors<- c("#f1eef6ff","#bdc9e1ff","#b3b3b3ff","#74a9cfff","#0570b0ff")
alluvial_justeduc <- ggplot(datos.justeduc, aes(x = ola, fill = just_educ, stratum = just_educ,
                             alluvium = idencuesta, y = porcentaje))+
    ggalluvial::geom_flow(alpha = .66) + 
    ggalluvial::geom_stratum(linetype = 0) +
    scale_y_continuous(labels = scales::percent) + 
    ylab(label = NULL) +
    xlab(label = NULL) + 
    theme(#legend.position = 'top',
          legend.title = element_blank(),
          plot.caption = element_text(hjust = 1)) +
    scale_fill_manual(values = colors) +
    geom_shadowtext(data = etiquetas.justeduc, 
              aes(label = ifelse(porcentaje > 0 , scales::percent(porcentaje, accuracy = .1),"")),
              position = position_stack(vjust = .5),
              show.legend = FALSE,
              size = 4,
              color = rep('white'),
              bg.colour='grey30')+
  scale_x_discrete(labels = c(2016, 2017, 2018, 2019, 2022)) +
  labs(caption = "Source: own elaboration with pooled data from ELSOC 2016-2022 (n = 8042)")

@@

ggsave(alluvial_justeduc, file="output/graphs/alluvial_dep.png", height = 8, width = 7)
```

```{r bivariate-plots}
df_study1 <- df_study_long_t6_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, des_perc, merit_effort, merit_talent,
                                               educ, quintil1:sexo) %>% na.omit()
merit_plot <- df_study1 %>% 
  select(merit_effort, merit_talent, des_perc, just_educ) %>% 
  sjPlot::plot_stackfrq(weight.by = df_study1$ponderador_long_total,
                        expand.grid =TRUE,
                      geom.colors = "PuBu",
                      show.total = FALSE, 
                      vjust=rep(c("bottom", "top", "bottom", "top", "bottom"),4),
                      legend.labels = c("Strongly disagree", "Disagree", "Neither agree
nor disagree", "Agree", "Strongly agree"),
                      axis.labels = c("Merit effort", "Merit talent", "Inequality 
perception", "Justification 
of 
educational inequality")
                      ) +
  theme_light(base_size = 16) +
  theme(legend.position="bottom", text = element_text(size = 14),
        plot.caption = element_text(hjust = 1)) +
  labs(caption = "Source: own elaboration with pooled data from ELSOC 2016-2022 (n = 8042)")
merit_plot

@@

## Crear el gráfico principal
years_plot <- ggplot(vars_years, aes(ola, value, color = variable, shape = variable, linetype = variable)) +
  theme_bw(base_size = 14) +
  geom_point(size = 4) +
  geom_line(aes(group = variable)) +
  geom_errorbar(aes(ymin = value_low, ymax = value_upp), width = 0.2) +
  ylab("Mean") +
  xlab("Wave") +
  ylim(1, 5) +
  scale_x_discrete(labels = categorias_x) +
  scale_color_manual(labels = categorias_z, name = "Variable", values =  c("#bdc9e1ff","#0570b0ff","#74a9cfff","#b3b3b3ff")) +
  scale_shape_manual(labels = categorias_z, name = "Variable", values = c("square", "circle", "triangle", "diamond")) +
  scale_linetype_manual(labels = categorias_z, name = "Variable", 
                        values = c("solid", "dashed", "dotted", "dotdash")) +  # Definir diferentes tipos de línea
   theme(legend.position = "none") +
  coord_cartesian(xlim = c(1, 6)) +  # Ampliar el eje x
  scale_x_discrete(labels = c(2016, 2017, 2018, 2019, 2022, ""))  # Personalizar etiquetas del eje x

@@

# Añadir etiquetas personalizadas
years_plot <- years_plot +
  geom_point(data = label_data, aes(label_x - 0.05, label_y, color = variable, shape = variable), size = 4) +  # Capa de puntos para los símbolos de forma
  geom_text(data = label_data, aes(label_x, label_y, label = variable), color = "black", hjust = 0, nudge_x = 0.05, nudge_y = 0, size = 4)  +
  labs(caption = "Source: own elaboration with pooled data from ELSOC 2016-2022 (n = 8042)")

@@

ggsave("output/graphs/years_plot.png", plot = years_plot, height = 6, width = 7, dpi = 300)

@@

```{r cor-plot, fig.dim=c(10,6)}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               sjPlot,
               sjmisc,
               summarytools,
               lavaan
               )
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))
df_study1 <- df_study_long_t6_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, des_perc, merit_effort, merit_talent,
                                               educ, quintil1:sexo) %>% na.omit()
# Full sample_______________________________________________________________________
mat_full<- 
df_study1 %>%
  # filter(ola==1) %>%
  select(just_educ, # distributive justice
         des_perc,
         merit_effort, merit_talent # meritocracy
         ) %>% 
  psych::mixedCor()

cor_full <- as.matrix(mat_full$rho)
diag(cor_full) = NA #set diagonal values to NA
# Set Row names of the matrix
rownames(cor_full) <- c("A. Justification of educational inequality",
                        "B. Inequality perception",
                     "C. People are rewarded for their efforts",
                     "D. People are rewarded for their intelligence")
#set Column names of the matrix
colnames(cor_full) <-c("(A)", "(B)","(C)","(D)")
#Plot the matrix using corrplot
png("output/graphs/corr.png",width=600,height=300, pointsize = 10)
corrplot::corrplot(cor_full,
  method = "color",
  addCoef.col = "#000390",
  type = "upper",
  tl.col = "black",
  col=colorRampPalette(c("white","#0068DC"))(12),
  bg = "white",
  na.label = "-")
# Agregar caption
grid::grid.text("Source: own elaboration with pooled data 
from ELSOC 2016-2022 (n = 8042)", x = 0.01, y = 0.05, just = "left", gp = grid::gpar(fontsize = 10, col = "black"))
dev.off()
# Wave 1_______________________________________________________________________
mat_1<- 
df_study1_long_comunas %>%
  filter(ola==1) %>%
  select(just_educ, # distributive justice
         merit_effort, merit_talent, # meritocracy
         ahead_family, ahead_ambition, ahead_educ, ahead_hardwork # go ahead
         ) %>% 
  psych::mixedCor()

@@

omit <- "(education)|(ess)"
texreg::htmlreg(list(educ0, educ1, educ2, educ3, educ4, educ5, educ6),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. <br>
Note: Model 3 to 7 are controlled by educational level, and subjective social status with no significant effects.", 
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave 2017 <br> <i>(Ref. Wave 2016)</i>",
                                      "Wave 2018",
                                      "Wave 2019",
                                      "Wave 2022",
                                      "Wave",
                                      "Wave^2",
                                      "Quintile 2 <br> <i>(Ref. Quintile 1)</i>",
                                      "Quintile 3",
                                      "Quintile 4",
                                      "Quintile 5",
                                      "Quintile NA",
                                      "Age 30-49 <br> <i>(Ref. 18-29)</i>",
                                      "Age 50-64",
                                      "Age 65 o más",
                                      "Gender <br> <i>(Ref. Male)</i>",
                                      "Pol. pos: Center <br> <i>(Ref. Left)</i>",
                                      "Pol. pos: Right",
                                      "Pol. pos: Does not identify",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: Effort" ),
                custom.gof.names = c("AIC",
                                     "BIC",
                                     "Log Likelihood",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Residual"),
                file = "output/tables/table1-individuales-pond-v2.html")
          #omit.coef = omit

@@

# Hipotesis
#h1b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort"
h2b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+merit_effort+merit_effort*ola+merit_effort*ola_2"
h3b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+merit_talent+merit_talent*ola+merit_talent*ola_2"
h4b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+des_perc*ola+des_perc*ola_2"
#h5b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*pos_id"
#h6b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*sexo"
#h7b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*quintil1"
#h8b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*edad"

# A. justification educational inequality
#educ1 <- lmer(formula(paste0("just_educ~",h1b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ2 <- lmer(formula(paste0("just_educ~",h2b,"+(ola+ola_2+merit_effort|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ3 <- lmer(formula(paste0("just_educ~",h3b,"+(ola+ola_2+merit_talent|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ4 <- lmer(formula(paste0("just_educ~",h4b,"+(ola+ola_2+des_perc|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ5 <- lmer(formula(paste0("just_educ~",h5b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ6 <- lmer(formula(paste0("just_educ~",h6b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ7 <- lmer(formula(paste0("just_educ~",h7b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ8 <- lmer(formula(paste0("just_educ~",h8b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)

# table 3: interacciones
omit <- "(education)|(ess)|(quintil1)|(edad)|(sexo)|(pos_id)"
texreg::htmlreg(list(educ2,educ3,educ4),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. <br>
Note: All the models are controlled by educational level, income quintile, subjective social status, age, gender and political position",
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave",
                                      "Wave^2",
                                      "Merit: Effort",
                                      "Wave * Merit: Effort",
                                      "Wave^2 * Merit: Effort",
                                      "Merit: Talent",
                                      "Wave * Merit: Talent",
                                      "Wave^2 * Merit: Talent",
                                      "Inequality perception",
                                      "Wave * Inequality perception",
                                      "Wave^2 * Inequality perception"
                                      ),
                custom.gof.names = c("AIC", "BIC", "Log Likelihood",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Individuals Wave",
                                     "Var: Individuals Wave^2",
                                     "Var: Individuals Merit: Effort",
                                     "Cov: Individuals (Intercept) Wave",
                                     "Cov: Individuals (Intercept) Wave^2",
                                     "Cov: Individuals (Intercept) Merit: Effort",
                                     "Cov: Individuals Wave Wave^2",
                                     "Cov: Individuals Wave Merit: Effort",
                                     "Cov: Individuals Wave^2 Merit: Effort",
                                     "Var: Residual",
                                     "Var: Individuals Merit: Talent",
                                     "Cov: Individuals (Intercept) Merit: Talent",
                                     "Cov: Individuals Wave Merit: Talent",
                                     "Cov: Individuals Wave^2 Merit: Talent",
                                     "Var: Individuals Inequality perception",
                                     "Cov: Individuals (Intercept) Inequality perception",
                                     "Cov: Individuals Wave Inequality perception",
                                     "Cov: Individuals Wave^2 Inequality perception"
                                     ),
                file = "output/tables/table3-interac_pond.html")
          #omit.coef = omit
